\thetitle

### 2013-04-13 tfpie/tfpie.tex
Intro CCIS acronym.
Elim some industrials.

\item from a pedagogical programming environment to an industrial
programming environment (Eclipse),

@@

At Northeastern, the College of Computer \& Information Science
requires a four course introductory sequence in the first year.  The
first semester features both a course on discrete mathematics as well
as an introduction to programming following the \emph{How to Design
  Programs} curriculum.  The second semester follows with a course on
object-oriented programming and one featuring formal reasoning about
programs, both on paper and with the ACL2 theorem
prover~\cite{dvanhorn:Kaufmann2000ComputerAided}.

@@

After our course, our students should both (a) be prepared for
subsequent courses in the curriculum, which expect familiarity with
Java and standard Java libraries, (b) be prepared for co-ops in which
they will use industrial-strength languages and tools which will
almost certainly be object-oriented.  More significantly, we aim to
teach the key insights behind the object-oriented approach to program
design.

>>>>

\item from a pedagogical programming environment to a professional
programming environment (Eclipse),

@@

At Northeastern, the College of Computer \& Information Science (CCIS)
requires a four course introductory sequence in the first year.  The
first semester features both a course on discrete mathematics as well
as an introduction to programming following the \emph{How to Design
  Programs} curriculum.  The second semester follows with a course on
object-oriented programming and one featuring formal reasoning about
programs, both on paper and with the ACL2 theorem
prover~\cite{dvanhorn:Kaufmann2000ComputerAided}.

@@

After our course, our students should both (a) be prepared for
subsequent courses in the curriculum, which expect familiarity with
Java and standard Java libraries, (b) be prepared for co-ops in which
they will use professional-grade languages and tools which will
almost certainly be object-oriented.  More significantly, we aim to
teach the key insights behind the object-oriented approach to program
design.
